\documentclass{resume}

\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Oghenekparobor Eminokanju}

\address{\href{mailto:robor.eminokanju@gmail.com}{robor.eminokanju@gmail.com} \\ 
\href{https://www.linkedin.com/in/aaron-eminokanju-ab9038180/}{LinkedIn} \\ 
\href{https://my-portofolio-1ab2d.web.app/}{My Portfolio}} 

\begin{document}

%----------------------------------------------------------------------------------------
% SUMMARY
%----------------------------------------------------------------------------------------

\begin{rSection}{SUMMARY}
Rust Developer and Blockchain Engineer specializing in Solana ecosystem development, DeFi architecture, and escrow automation. Over 6 years of experience designing secure, high-performance applications in fintech, blockchain, and Web3 infrastructure.

Expert in building Solana programs, meta-transaction relayers, and scalable Rust backends with a strong focus on security, performance, and decentralized finance. Experienced in launching DeFi platforms and contributing to open-source Solana-based tools.
\end{rSection}

%----------------------------------------------------------------------------------------
% EDUCATION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Engineering, Structural Engineering}, University of Benin \hfill {2015 - 2021} \\
{\bf Ackee School of Solana, 9-week Developer Program} \hfill {July 2025 - Sept 2025}

\end{rSection}

%----------------------------------------------------------------------------------------
% TECHNICAL SKILLS
%----------------------------------------------------------------------------------------

\begin{rSection}{TECHNICAL SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages & Rust, Dart, TypeScript, Kotlin, Swift, PHP \\
Blockchain & Solana, Web3, SPL Tokens, Anchor, NFT, DeFi, Escrow Smart Contracts \\
Frameworks & Actix, Rocket, Tokio, Flutter, SwiftUI, Laravel \\
API & RESTful, GraphQL, gRPC, WebSockets \\
Architecture & Microservices, Clean Architecture, MVVM \\
Database & PostgreSQL, MySQL, MongoDB \\
Testing & proptest, Unit \& Integration Testing \\
DevOps & Docker, Kubernetes, CI/CD (GitHub Actions, Fastlane, Bitbucket) \\
Security & OWASP, Penetration Testing, Memory Safety (Rust) \\
\end{tabular}\\
\end{rSection}

%----------------------------------------------------------------------------------------
% EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{EXPERIENCE}

\textbf{Rust / Solana Developer} \hfill Mar 2025 - Present\\
\textbf{Guava Finance} \hfill \textit{Lagos, NG}
\begin{itemize}
    \item Developed and deployed a reward-based mint program that rewards loyalty for Guava.
    \item Built a self-custody Solana wallet that enables users to spend crypto like cash.
    \item Implemented a meta-transaction relayer that sponsors user transaction fees on Solana.
    \item Implemented support for token swaps across SPL tokens and Token-2022 standard.
\end{itemize}

\textbf{Rust Developer} \hfill Sept 2023 - Nov 2024\\
\textbf{Excrow} \hfill \textit{Remote}
\begin{itemize}
    \item Built escrow-as-a-service APIs and Solana programs powering Web3 financial integrations for banks and fintechs.
    \item Designed and deployed Rust-based smart contracts for secure on-chain escrow settlements.
    \item Integrated Telegram bots and REST APIs for end-user access to decentralized escrow transactions.
\end{itemize}

\textbf{Senior Mobile Engineer} \hfill Apr 2022 - Mar 2025\\
\textbf{Renmoney Microfinance Bank} \hfill \textit{Lagos, NG}
\begin{itemize}
    \item Led the redevelopment of Renmoney’s mobile app, integrating blockchain-backed payment infrastructure.
    \item Improved app performance and compliance while reducing downtime by 3\%.
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
% PROJECTS
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Pollinet (Solana Foundation Grant).} {Developing an offline Solana mesh network enabling transactions without internet, leveraging Bluetooth-based device communication.\href{https://pollinet.lovable.app}{(View)}}
\item \textbf{Guava Wallet.} {Built a Solana-based DeFi wallet for USDC with escrow, meta-transactions, and relayer services.\href{https://guava.finance}{(View)}}
\item \textbf{Excrow} {Engineered an escrow-as-a-service API and Telegram bot for Web3 escrow automation.\href{https://excrowbot-web.vercel.app}{(View Bot)} \href{https://de-escrow.vercel.app/}{(View Defi)}}
\item \textbf{Renmoney Core Banking.} {Led the rebuild of Renmoney’s mobile banking app, increasing reliability and transaction throughput. \href{https://play.google.com/store/apps/details?id=com.renmoney.android}{(View on Play Store)}}
\end{rSection}

%----------------------------------------------------------------------------------------
% CERTIFICATIONS
%----------------------------------------------------------------------------------------

\begin{rSection}{CERTIFICATIONS}
\vspace{-1.25em}
\item \textbf{ISC2} — Certified in Cybersecurity \href{https://www.credly.com/badges/6cbdbdce-2652-4dfe-8d0b-e1a038abb231/linked_in_profile}{(View Credential)}
\end{rSection}

%----------------------------------------------------------------------------------------
% COMMUNITY & LEADERSHIP
%----------------------------------------------------------------------------------------

\begin{rSection}{Community \& Leadership} 
\begin{itemize}
    \item Mentor for the \href{https://blip.school/}{BlipSchool} Mobile Program (100+ mentees).
    \item Contributor to Solana open-source ecosystem and technical writer on Rust and Web3.
    \item Active participant in Solana and DeFi developer communities.
\end{itemize}
\end{rSection}

\end{document}
